Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2020-03-26 analysis/paper/Rmd/hotspot-one-chromosome-timbr.Rmd
fixed inputted col name

```{r}
pheno <- cbind(hot_local, hot_nonlocal)
set.seed(3411192) # to ensure getting the same samples with TIMBR
future::plan("multiprocess")
t_out <- hot_annot %>%
  dplyr::filter(pos <= hot_upper, pos >= hot_lower) %>%
  dplyr::mutate(marker_index = purrr::map_int(.x = pos, .f = function(x) which(map[[{{hot_chr}}]] == x))) %>%
  dplyr::mutate(t_out = furrr::future_pmap(.l = list(lodcolumn, marker_index), .f = function(lodcolumn, marker_index){
    phe_pre <- pheno[ , colnames(pheno) == lodcolumn, drop = FALSE]
    phe <- phe_pre[!is.na(phe_pre), , drop = FALSE]
    pr_pre <- gp[[1]][, , marker_index] # use first (and only!) entry in gp
    pr <- pr_pre[rownames(pr_pre) %in% rownames(phe), ]
    cov_pre <- cbind(1, covar)
    cov_pre2 <- cov_pre[rownames(cov_pre) %in% rownames(phe), ]
    cov <- qtl2:::drop_depcols(cov_pre2)
    TIMBR::TIMBR(y = phe, 
                 prior.D = list(P = pr, 
                                A = mcv.data$prior.D$A, # works for autosomes
                                fixed.diplo = FALSE), 
                 prior.M = prior_M1, 
                 samples = 10000, 
                 samples.ml = 10000,
                 Z = cov, 
                 verbose = TRUE
                 )  
}))
dim(t_out)
saveRDS(t_out, here::here("analysis", "data", "derived_data", "timbr-chr{{hot_chr}}-10ksamples-M1.rds"))
```

>>>>

```{r}
pheno <- cbind(hot_local, hot_nonlocal)
set.seed(3411192) # to ensure getting the same samples with TIMBR
future::plan("multiprocess")
t_out <- hot_annot %>%
  dplyr::filter(pos <= hot_upper, pos >= hot_lower) %>%
  dplyr::mutate(marker_index = purrr::map_int(.x = pos, .f = function(x) which(map[[{{hot_chr}}]] == x))) %>%
  dplyr::mutate(t_out = furrr::future_pmap(.l = list(annot.id, marker_index), .f = function(lodcolumn, marker_index){
    phe_pre <- pheno[ , colnames(pheno) == lodcolumn, drop = FALSE]
    phe <- phe_pre[!is.na(phe_pre), , drop = FALSE]
    pr_pre <- gp[[1]][, , marker_index] # use first (and only!) entry in gp
    pr <- pr_pre[rownames(pr_pre) %in% rownames(phe), ]
    cov_pre <- cbind(1, covar)
    cov_pre2 <- cov_pre[rownames(cov_pre) %in% rownames(phe), ]
    cov <- qtl2:::drop_depcols(cov_pre2)
    TIMBR::TIMBR(y = phe, 
                 prior.D = list(P = pr, 
                                A = mcv.data$prior.D$A, # works for autosomes
                                fixed.diplo = FALSE), 
                 prior.M = prior_M1, 
                 samples = 10000, 
                 samples.ml = 10000,
                 Z = cov, 
                 verbose = TRUE
                 )  
}))
dim(t_out)
saveRDS(t_out, here::here("analysis", "data", "derived_data", "timbr-chr{{hot_chr}}-10ksamples-M1.rds"))
```
